### 2018-07-03 pack/prv/opt/tokipona/aux/article/acm/samplebody-journals.tex
terminada a classe de sintese de fragmentos e poemas em toki pona

\subsection{Synthesis of text}\label{synth}
Such counting exercises are also useful
for (semi-)automated writing through scripting.
The syntax organizes the words in larger structures.
The rhymes are very restricted and sonorities are
bounded by the small vocabulary and simple syntax.
There are some specific tasks for achieving texts,
such as finding the number of syllables considering the elisions,
or handling interaction of the writer with the script
to choose sentences or verses or stanzas.
The same package~\cite{tokipona}
has capabilities for synthesizing TP text.
On its most basic level, these routines yield
noun, verb and prepositional phrases,
and sentences.
They also aim at making larger scale texts
by assuring the use of specific words (to entail context),
e.g. to assist the creation of short narratives,
and by employing stylistic outlines for poems.

@@

Automatic and randomized synthesis of texts in TP is particularly
useful because of the reduced vocabulary where each word is related
to a broad semantic field.
Ideas often make sense in unexpected ways, and thus
the synthesis yields a procedure to 
explore the semantic possibilities within TP.
One might object that the resulting texts are unusual 
and even consider that they often hold insubstantial or unsound meaning.
I advocate that these unexpected formations are desirable
for exploring the possibilities of the language and of thought,
and for artistic endeavors.
Also, to obtain texts which one finds usual or satisfactory
in more strict or personal terms, such a person might just write
them normally.

>>>>

\subsection{Synthesis of text}\label{synth}
Such counting exercises are also useful
for (semi-)automated writing through scripting.
The syntax organizes the words in larger structures.
The rhymes are very restricted and sonorities are
bounded by the small vocabulary and simple syntax.
There are some specific tasks for achieving texts,
such as finding the number of syllables considering the elisions,
or handling interaction of the writer with the script
to choose sentences or verses or stanzas.
The package~\cite{tokipona}, herein presented, also
has capabilities for synthesizing TP text.
On its most basic level, these routines yield
noun, verb and prepositional phrases,
and sentences.
They also aim at making larger scale texts
by assuring the use of specific words (to entail context),
e.g. to assist the creation of short narratives,
and by employing stylistic outlines for poems.

@@

Automatic and randomized synthesis of texts in TP is particularly
useful because of the reduced vocabulary where each word is related
to a broad semantic field.
Ideas often make sense in unexpected ways, and thus
the synthesis yields a procedure to 
explore the semantic possibilities within TP.
One might object that the resulting texts are unusual 
and even consider that they often hold insubstantial or unsound meaning.
I advocate that these unexpected formations are desirable
for exploring the possibilities of the language and of thought,
and for artistic endeavors.
Also, to obtain texts which one finds usual or satisfactory
in more strict or personal terms, such a person might just write
them normally or use the synthesized texts as raw material.
